|

### 2020-09-11 paper.Rmd
add second example for mouse data

We tour the first five PCs (approximately 20% of the variance in expression),
on a weighted subsample of cells based on their cluster membership - 4,590 cells. When running the sage display, we set $\gamma = 3$ as the effective dimensionality of the data.

Using the default tour display, the highlighted cluster in dark green is obscured by points in nearby clusters as shown in figure \ref{fig:mouse} (left). Using the sage display, expands the center of projection, so the dark green cluster becomes more visible; the outlier cell that is far away from the rest of the clustered points is more apparent.

- better idea of size of cluster cause not bunching 
- rescale = FALSE, use principal components
- try multiple overlapping cluster example

@@

>>>>

We tour the first five PCs (approximately 20% of the variance in expression),
on a weighted subsample of cells based on their cluster membership - 4,590 cells. When running the sage display, we set $\gamma = 3$ as the effective dimensionality of the data. For the displays we have rescaled the PCs so they each have zero mean and unit variance.

Using the default tour display, the highlighted cluster in dark green is obscured by points in nearby clusters as shown in figure \ref{fig:mouse} (top). Using the sage display, expands the center of projection, so the dark green cluster becomes more visible; the outlier cell that is far away from the rest of the clustered points is more apparent.

@@

However, often we also want
to know clusters relative positions and cluster sizes. In the next example we colour points with two additional cluster labels that completly overlap in an ordinary principal components scatter plot.
